Towards a Complete Model of Mutation Selection Balance in Humans

### 2023-05-13 manuscript/manuscript.tex
para 2

As with most selection in the genome, selection on deleterious variation
process perturbs the allele frequencies of neighboring linked variation. This
reduces genetic variability around conserved segments and creates large-scale
spatial patterns in genetic diversity. These patterns are mediated by the
deleterious mutation rate, the strength of selection in conserved segments, and
the spatial distribution of recombination rates and conserved segments. Since
genome-wide recombination maps and putatively conserved segments are available
for many species, researchers have combined these with population genetic
theory to estimate the mutation rate and selection coefficients of deleterious
mutations, as well as the overall reduction in genetic variability due to the
negative selection process.

>>>>

Selection on both beneficial and deleterious alleles leads to 
perturbations in the allele frequency spectrum of neighboring, linked variation.
This phenomenon, known as linked selection, is a major force shaping patterns of
genetic variation along chromosomes \citep{Maynard_Smith1974-zr,Charlesworth1993-gb,Barton1998-aj,Gillespie2000-mh}.
As deleterious variation is clustered in functional portions of the genome,
we expect linked selection to reduce levels of diversity surrounding evolutionarily
conserved segments (e.g. genes, regulatory elements, etc.) 
and to shape large-scale spatial patterns in genetic diversity. 
This landscape of diversity is the product of a complex interplay between the
deleterious mutation rate, the local recombination rate, the strength of selection, and
the spatial distribution of conserved segments along a chromosome. 
Since genome-wide recombination maps and putatively conserved segments are available
for many species, there has been consistent effort to fit models of
linked selection to patterns of diversity to estimate population genetic
parameters such as the strength of selection and the deleterious mutation rate 
\citep{Hudson1995-pt,McVicker2009-ax},
the overall reduction in genetic variability due to the
selection on deleterious variants \citep{Elyashiv2016-vt,Murphy2022-sj},
and in some cases the rate of beneficial mutations \citep{corbett2015natural,Elyashiv2016-vt}.
